### 2021-09-06 input/experiments.tex
keywords

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are more expensive than add operations. Indeed, the
top part of the figure shows that after 21 seconds, when the
experiment involves removals, traffic includes both $\alpha$'s and
$\delta$'s. The latter aims at removing stale information and
triggering competition while the former aims at updating shortest
paths. As corollary, the convergence time increases, for $\delta$
messages must reach the partition borders before sound competitors
propagate their partition. It is worth noting that this delete
operation involves concurrency: removals continue to propagate while
the competition is already partially triggered and propagating.

@@

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 adds and the 100 deletes, \processes
do not generate traffic anymore. Being reactive, \NAME has no overhead
when there is no operation in the system. In other words, \NAME's
overhead actually depends on its usage.

>>>>

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are more expensive than add operations. Indeed, the
top part of the figure shows that after 21 seconds, when the
experiment involves removals, traffic includes both $\alpha$'s and
$\delta$'s. The latter aims at removing stale information and
triggering competition while the former aims at updating shortest
paths. As corollary, the convergence time increases, for $\delta$
messages must reach the partition borders before sound competitors
propagate their partition. It is worth noting that this delete
operation involves concurrency: removals still propagate while
the competition has started. %%is already partially triggered and propagating.

@@

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 adds and the 100 deletes, \processes
do not generate traffic anymore. Being reactive, \NAME has no overhead
when there is no operation in the system. \NAME's overhead actually
depends on its usage.
